%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Postdoctoral researcher \& Bioinformatician} % Job title
    {Center for Medical Genetics Ghent} % Organization
    {Ghent, Belgium} % Location
    {Dec. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researching DNA secondary structures and replicative
            stress in neuroblastoma and pan-cancer.}
        \item {Researched classification algorithms (decision trees,
            neuronal networks) to improve outcome prediction of
            neuroblastoma patients.}
        \item {Multivariate ranking of biomarkers for patient stratification.}
      \item {Built and deployed overall bioinformatics platform
          utilizing Docker container, focusing on high-availability,
          ease of use, and auto-scaling.}
      \item {Implementing a network analysis tool with random restart
          walk in collaboration with UGent systems biology team.}
      \item {Supervising PhD students. Assisting them in constructing
          research hypotheses, experimental design, and data
          analysis.}
      \item {Assisting in bioinformatics course for graduate
          students.}
      \item {Data processing experience with ChIP seq, ATAC seq,
          shallow whole genome sequencing.}
      \item {Preparing applications for ethics commission.}
      %\item {Complying with regulations for the accredited medical
      %    genetics laboratory in which our research department was located.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Postdoctoral fellow} % Job title
    {Computational Bioscience Research Center, KAUST} % Organization
    {Thuwal, Saudi Arabia} % Location
    {Jul. 2018 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applying text mining and natural language processing to the medical literature, to extract knowledge for the advancement of medical research, with special attention to cancer research.}
        \item {Extracting useful information from big data in biomedicine through use of machine learning and deep neural networks.}
        \item {Using graph methods on the knowledge graphs we
            generate, to derive novel insights.}
      \item {Supervising master and PhD-students, coordinating
          scientific projects.}
      \item {Teaching assistant in the course "AI in bioinformatics."}
      \item {Teaching assistant for the 5-day workshop "Women Machine
          Learning Bootcamp 2019."}
      \item {Fire warden and qualified first-aider.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Forensic researcher} % Job title
    {Laboratory for pharmaceutical biotechnology} % Organization
    {Ghent, Belgium} % Location
    {Jun. 2015 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on massively parallel sequencing projects.}
        \item {Discussing the minimal nomenclature requirements within
          the forensic DNA commission.}
        \item {Setting up international collaborations in the field of
            forensics.}
        \item {Assisting the initiation of a pharmacogenomics project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bioinformatics intern} % Job title
    {Illumina} % Organization
    {San Diego, USA} % Location
    {Mar. 2014 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing apps for the BaseSpace platform.}
        \item {Collaborating with core BaseSpace developers to improve
            their platform.}
        \item {Experience with Docker, D3, scrum, test driven development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PhD student } % Job title
    {Laboratory for pharmaceutical biotechnology} % Organization
    {Ghent, Belgium} % Location
    {May. 2011 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed software tools to assist forensic community
            transitioning to use of sequencing for DNA profiling}
        \item {Implemented a RESTful API server for forensic allele
            nomenclature.}
        \item {Data processing experience with Roche 454, Illumina,
            IonTorrent, Nanopore for genomics, methylomics, and
            trancriptomics. Mass spec data experience for proteomics.}
        \item {Programming laboratory robot for automated forensic
            sample processing.}
        \item {System and network administration for accredited
            forensic laboratory.}
        %\item {Working together with quality manager for internal audits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Webmaster} % Job title
    {\emph{several organizations}} % Organization
    {Ghent, Belgium} % Location
    {2005 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learning different web languages: PHP, JavaScript, HTML, CSS.}
        \item {Implementing the content management system Drupal.}
      \end{cvitems}
    }

\end{cventries}
